|

### 2021-12-03 03-Chp-Systematic-Review-Methods.Rmd
End of day:

<!-- IDEA Stratify by ApoE4 genotype -->

@@

## Lay summary

Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question. Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.

This chapter presents the methods used to perform a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes. In addition, the review examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes. The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading).

<!----------------------------------------------------------------------------->
## Introduction {#sys-rev-intro}

@@

#### Analysis overview

@@

The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.  As such, different reported effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] However if the outcome is rare, as is the case for dementia outcomes, the estimated odds, risk and hazard ratios will approximate each other.[@vanderweele2020] As such, I did not stratify the analyses by reported effect measure.

>>>>

<!-- IDEA Stratify by _ApoE4_ genotype -->

@@

::: {.laybox data-latex=""}
## Lay summary {-}

Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question. Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results. 
&nbsp;

This chapter presents the methods used to perform a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes. In addition, the review examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes. The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading).
:::

## Introduction {#sys-rev-intro}

@@

#### Analysis overview {#sys-rev-analysis-overview}

@@

The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc.) are not directly interchangeable in the context of systematic review.  As such, different reported effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] However if the outcome is rare, as is the case for dementia outcomes, the estimated odds, risk and hazard ratios will approximate each other.[@vanderweele2020] As such, I did not stratify the analyses by reported effect measure.

### 2021-12-03 06-Chp-IPD-Analysis.Rmd
End of day:

# Individual participant data meta-analysis of blood lipid levels and dementia outcomes {#ipd-heading}
\minitoc <!-- this will include a mini table of contents-->

@@

## Lay Summary

@@

The results from the main effect analysis across the varying lipid fractions on each dementia,  considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively. There was very weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r tri_vasdem`).

>>>>

# Individual participant data meta-analysis of blood lipid levels and dementia outcomes {#ipd-heading}

\minitoc <!-- this will include a mini table of contents-->

@@

## Lay Summary {-}

@@

The results from the main effect analysis across the varying lipid fractions on each dementia,  considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively. There was very weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`).
